---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

```{r quiz1_1}
quiz(
  question("Wofuer ist das Alter einer Versuchsperson ein Beispiel?",
    answer("Datensatz"),
    answer("Datenbank"),
    answer("Statistik"),
    answer("Daten", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_2, echo = FALSE}
quiz(
  question("Was sind Vorteile digitaler Datenanalyse?",
    answer("Es können große Datensätze verarbeitet werden", correct = TRUE),
    answer("Kommt zu besseren Ergebnissen"),
    answer("Es werden weniger Flüchtigkeitsfehler gemacht", correct = TRUE),
    answer("Iterationsbasierte Verfahren möglich", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_3, echo = FALSE}
quiz(
  question("Was sind Kriterien für wissenschaftliche Hypothesen?",
    answer("Falsifizierbarkeit", correct = TRUE),
    answer("Finalsatz"),
    answer("empirisch untersuchbar", correct = TRUE),
    answer("Konditionalsatz", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_4, echo = FALSE}
quiz(
  question("Welche sind wissenschaftliche Hypothesen?",
    answer("Manche depressive Patienten schlafen schlechter.", correct = TRUE),
    answer("Zwangspatienten machen häufiger sauber, als gesunde Kontrollprobanden."),
    answer("Es gibt Menschen, die zum pathologischen Grübeln neigen."),
    answer("Es besteht ein Zusammenhand zwischen Angst und sozialer Netzwerkgröße.", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_5, echo = FALSE}
quiz(
  question("Bei welchen handelt es sich um gerichtete Hypothesen?",
    answer("Frauen sind besser als Männer in mentalen Rotationsaufgaben.", correct = TRUE),
    answer("Es besteht ein Zusammenhang zwischen Schlafproblemen und Agitiertheit."),
    answer("Wenn man mehr Stress ausgesetzt ist entwickelt man leichter eine Psychose", correct = TRUE),
    answer("Es besteht ein negativer Zusammenhang zwischen Vermeidungsverhalten und beruflichem Erfolg.", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_6, echo = FALSE}
quiz(
  question("Gewicht [kg] ist eine..",
    answer("stetige Variable", correct = TRUE),
    answer("latente Variable"),
    answer("dichotome Variable"),
    answer("manifeste Variable", correct = TRUE), allow_retry = TRUE
  )
    )
```

```{r quiz1_7, echo = FALSE}
quiz(
  question("Welche der folgenden sind latente Variablen?",
    answer("Persönlichkeit", correct = TRUE),
    answer("Extraversion", correct = TRUE),
    answer("Zittern"),
    answer("Blutdruck"),
    answer("Einsamkeit", correct = TRUE)
    , allow_retry = TRUE
  )
    )
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

